\documentclass[10 pt]{article}
\usepackage[a4paper,bottom = 10mm,left = 0.56in,right = 0.56in,top = 6.4mm]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{array}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{textcomp}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{verbatim}
\newcommand{\xfilll}[2][1ex]{
\dimen0=#2\advance\dimen0 by #1
\leaders\hrule height \dimen0 depth -#1\hfill}
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}
\renewcommand\labelitemi{\raisebox{0.4ex}{\tiny$\bullet$}}
\renewcommand{\labelitemii}{$\cdot$}
\pagenumbering{gobble}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    % pdftitle={Overleaf Example},
    % pdfpagemode=FullScreen,
    }
\begin{document}
\vspace*{42mm} 
\hspace{-14pt}Pursuing \textbf{Honors} in \textbf{Computer Science} and {\bf Minor} in \textbf{Machine Intelligence and Data Science}
\vspace{-10pt}
\section*{\textcolor{blue}{\LARGE Scholastic Achievements}\xfilll[0pt]{0.5pt}}
\vspace{-8pt}
\begin{itemize}[itemsep = -0.75 mm, leftmargin=*]
\item Secured \textbf{All India Rank 232} in \textbf{JEE Advanced} among over 150 thousand candidates \hfill{\sl \small(2021)}
\item Secured \textbf{first position} in \textbf{JLR Hackathon 4.0} among over 80 teams. \hfill{\sl \small(2024)}

\end{itemize}
\vspace{-22pt}
\section*{\textcolor{blue}{\LARGE Internship}\xfilll[0pt]{0.5pt}}
\vspace{-8pt}
{\fontfamily{lmss}\selectfont
		\textbf{{Jaguar Land Rover}}\hfill{\sl \small (May-July 2024)}\\
	}{\it Software Development \textbar} {\it Company Internship}\\

		\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item  Automated data extraction from \textbf{GitLab, Jira}, and \textbf{Snyk} using \textbf{APIs} and \textbf{GCP} Cloud Functions of \textbf{SDV} Project.
            \item Created \textbf{Tableau dashboards} to visualize data insights, linking \textbf{Jira tickets} with \textbf{GitLab commits} for analysis.
            \item Leveraged \textbf{Microsoft PHI3} for suggestions, code ratings, and tracking requirements completion in \textbf{Jira} and \textbf{GitLab}.
		
	\end{itemize}
\vspace{-22pt}
\section*{\textcolor{blue}{\LARGE Key Projects}\xfilll[0pt]{0.5pt}}
{\fontfamily{lmss}\selectfont
		\textbf{{Fake News Detection}}\hfill{\sl \small (Sept-Oct 2023)}\\
	}{\it Guide: Prof. Pushpak Bhattacharyya \textbar} {\it Course Project: Natural Language Processing}\hfill{\sl \small IIT Bombay}\\

		\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
      \item Implemented a \textbf{fake news detection} model using \textbf{statistical, neural}, and \textbf{external} text classification features.
      \item Enhanced \textbf{stance detection} by integrating \textbf{skip-thought} vectors, \textbf{TF-IDF}, and heuristic-based external features.
      \item Optimized model with \textbf{cross-entropy loss}, classifying news into agree, disagree, discuss, and unrelated.
	\end{itemize}
{\fontfamily{lmss}\selectfont
		\textbf{{Image Captioning}}\hfill{\sl \small (Sept-Oct 2023)}\\
	}{\it Guide: Prof. Preethi Jyothi \textbar} {\it Course Project: Artificial Intelligence and Machine Learning}\hfill{\sl \small IIT Bombay}\\
		\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
    \item Developed an image captioning model using \textbf{PyTorch} with visual attention for precise and accurate caption generation.
    
    \item Implemented \textbf{Bahdanau attention} in the model to focus on key image areas for enhanced caption quality.
    \item Evaluated the model performance using \textbf{BLEU} and \textbf{METEOR} scores for quality and accuracy assessment.
	\end{itemize}
{\fontfamily{lmss}\selectfont
		\textbf{{Neural Quest}}\hfill{\sl \small (May-july 2023)}\\
	}{\it Seasons of Code}\hfill{\sl \small Institute Technical Council, IIT Bombay}\\

		\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Developed image prediction model for \textbf{MNIST} dataset from scratch using \textbf{NumPy} and \textbf{matplotlib} libraries
  and obtained an accuracy of \textbf{93} \% and \textbf{95} \% using \textbf{PyTorch} and \textbf{torchvision} evaluated on number of correct labels.
		\item Implemented classification model for CIFAR-10 using \textbf{convolutional neural network} and got accuracy of \textbf{81.28} \%.
	\end{itemize}
{\fontfamily{lmss}\selectfont
		\textbf{{Sclp C-like Compiler}}\hfill{\sl \small (Jan-April 2024)}\\
	}{\it Guide: Prof. Uday Khedker \textbar} {\it Course Project: Implementation of Programming Languages}\hfill{\sl \small IIT Bombay}\\

		\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
  \item  Developed a \textbf{compiler} for a subset of C, supporting \textbf{functions, scope levels} and \textbf{control sequences}
\item Used \textbf{Lex} for tokenizing \& \textbf{Yacc} for {parsing} to construct \textbf{ASTs} and \textbf{Three Address Codes}
\item Designed \textbf{RTL} and \textbf{ASM} classes using \textbf{Object Oriented Programming paradigm} following \textbf{class hierarchies}
	\end{itemize}
{\fontfamily{lmss}\selectfont
		\textbf{{Rail Planner}}\hfill{\sl \small (Autumn 2022)}\\
	}{\it Guide: Prof. Supratik Chakraborty \textbar} {\it Course Project}\hfill{\sl \small IIT Bombay}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Implemented multiple \textbf{data structures} and \textbf{alogorithms} in C++, utilized each of them within suitable components.
\item Implemented {\bf graph} data structure to find the shortest route between two stations in the multi-rail network system.
\item Implemented an interface for rating and filtering system for the journey reviews using \textbf{Heap and Priority Queues}.
	\end{itemize}



 \vspace{-16pt}


\section*{\textcolor{blue}{\LARGE Technical Skills}\xfilll[0pt]{0.5pt}}
\vspace{-8pt}
\begin{tabular}{p{4.5cm} p{13.5cm}}
  \textbf{Programming:} &  C++, Python, Bash, Awk, Sed, Markdown, Java, Assembly, Prolog, FLTK\\
  \textbf{Software:} &  Git, \LaTeX, GDB, Sphinx, Doxygen, Jupyter, Docker, Wireshark, Gitlab , Jira, Snyk\\
  \textbf{Packages:} & NumPy, Matplotlib, FLTK, Pandas, Torchvision, Pytorch, API\\
\end{tabular}

\section*{\textcolor{blue}{\LARGE Extracurricular}\xfilll[0pt]{0.5pt}}
\vspace{-8pt}

% {\bf \large Creative Field}  \vspace{-4pt}
\begin{itemize}[itemsep = -0.75 mm, leftmargin=*]
\vspace{-2pt}
	\item Successfully completed a course under the \textbf{National Sports
	Organization(NSO)}
	\hfill{\sl (Autumn 2021)}
    \item Designed a flying model of an \textbf{RC plane} powered by \textbf{BLDC motor} 
	\hfill{\sl (Autumn 2022)}
	\item Completed \LaTeX{} course in \textbf{Learner's Space}
	\hfill{\sl (Summer 2022)}

\end{itemize}
\vspace{-2pt}
  



\end{document}

