\documentclass[10 pt]{article}
\usepackage[a4paper,bottom = 10mm,left = 0.56in,right = 0.56in,top = 6.4mm]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{array}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{textcomp}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{verbatim}
\newcommand{\xfilll}[2][1ex]{
\dimen0=#2\advance\dimen0 by #1
\leaders\hrule height \dimen0 depth -#1\hfill}
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}
\renewcommand\labelitemi{\raisebox{0.4ex}{\tiny$\bullet$}}
\renewcommand{\labelitemii}{$\cdot$}
\pagenumbering{gobble}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    % pdftitle={Overleaf Example},
    % pdfpagemode=FullScreen,
    }
\begin{document}
\vspace*{42mm} 
\hspace{-14pt}Pursuing \textbf{Honors} in \textbf{Computer Science} and {\bf Minor} in \textbf{Machine Intelligence and Data Science}
\vspace{-10pt}
\section*{\textcolor{blue}{\LARGE Scholastic Achievements}\xfilll[0pt]{0.5pt}}
\vspace{-8pt}
\begin{itemize}[itemsep = -0.75 mm, leftmargin=*]
\item Secured \textbf{All India Rank 232} in \textbf{JEE Advanced} among over 150 thousand candidates \hfill{\sl \small(2021)}

\end{itemize}
%\vspace{-19pt}

\vspace{-22pt}
\section*{\textcolor{blue}{\LARGE Key Projects}\xfilll[0pt]{0.5pt}}
{\fontfamily{lmss}\selectfont
		\textbf{{Neural Quest}}\hfill{\sl \small (May-july 2023)}\\
	}{\it Seasons of Code}\hfill{\sl \small Institute Technical Council, IIT Bombay}\\

		\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item  Researched, developed, implemented and evaluated diverse deep learning models for computer vision classification.
		\item Developed image prediction model for \textbf{MNIST} dataset from scratch using \textbf{NumPy} and \textbf{matplotlib} libraries
  and obtained an accuracy of \textbf{93} \% and \textbf{95} \% using \textbf{PyTorch} and \textbf{torchvision} evaluated on number of correct labels.
		\item Implemented classification model for CIFAR-10 using \textbf{convolutional neural network} and got accuracy of \textbf{81.28} \%.
	\end{itemize}
 {\fontfamily{lmss}\selectfont
		\textbf{{Blockchain Technology}}\hfill{\sl \small (May-july 2023)}\\
	}{\it Summer of Science}\hfill{\sl \small Institute Technical Council, IIT Bombay}\\

		\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item  Studied basics of blockchain technology, including Bitcoin transaction security and defense against potential attacks.
  \item Studied \textbf{selfish mining attacks, Slasher}, and \textbf{PoS} in blockchain, Slasher penalizes, PoS validates based on staking.
  \item Exploring consensus algorithms such as \textbf{PBFT} and \textbf{Raft}, understanding their role in achieving fault-tolerance and consensus in distributed systems.
	\end{itemize}
 	{\fontfamily{lmss}\selectfont
		\textbf{{IPCP Prefetcher for Spec and Graph Workloads}}\hfill{\sl \small (spring 2023)}\\
	}{\it Guide: Prof. Biswa \textbar} {\it Course Project:  Computer Architecture}\hfill{\sl \small IIT Bombay}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Obtained an average 1.05x speedup in \textbf{IPC} on various traces by enhancing the \textbf{IPCP prefetcher} using \textbf{champsim}.
		\item Increased \textbf{cache hit rates} and \textbf{prefetch accuracy} in caches through customized modifications in IPCP prefetcher.
	\end{itemize}
{\fontfamily{lmss}\selectfont
		\textbf{{Cinema A to Z}}\hfill{\sl \small (Autumn '22)}\\
	}{\it Guide: Prof. Kavi Arya \textbar} {\it Course Project: Software Systems Lab}\hfill{\sl \small IIT Bombay}\\

		\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Developed a comprehensive movie and TV show database by utilizing \textbf{web scraping} techniques on IMDb, Rotten Tomatoes, extracting crucial data such as titles, ratings, genres, user reviews, similar movies, plot and cast information.
		\item Designed, executed, and successfully deployed an \textbf{SQL} database to efficiently store and manage the scraped data.
		\item Constructed a user-friendly website using \textbf{PHP}, allowing users to create accounts, log in, and personalize their movie watching experience by liking, watching, and adding or removing movies, TV shows, and anime to their watchlist.
		% \item  Demonstrated proficiency in front-end development by designing an intuitive and visually appealing interface, enabling users to navigate through the vast collection of movies, TV shows, and anime, and interact with their  watchlist.
	\end{itemize}
{\fontfamily{lmss}\selectfont
		\textbf{{Rail Planner}}\hfill{\sl \small (Autumn 2022)}\\
	}{\it Guide: Prof. Supratik Chakraborty \textbar} {\it Ongoing Course Project}\hfill{\sl \small IIT Bombay}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Implemented multiple data structures and alogorithms in C++, including \textbf{Linked Lists, Dictionaries, Binary Search Trees, Tries},\textbf{Priority Queues}, and \textbf{BFS, DFS, KMP} and utilized each of them within suitable components.
\item Implemented {\bf graph} data structure to find the shortest route between two stations in the multi-rail network system.
\item Implemented an interface for rating and filtering system for the journey reviews using \textbf{Heap and Priority Queues}.
	\end{itemize}
\vspace{\baselineskip}
\vspace{-16pt}

\section*{\textcolor{blue}{\LARGE Technical Skills}\xfilll[0pt]{0.5pt}}
\vspace{-8pt}
\begin{tabular}{p{4.5cm} p{13.5cm}}
  \textbf{Programming:} &  C++, C, Python, Java, Bash, Awk, Sed \\
  \textbf{Web Development:} & HTML, CSS, Bootstrap, JavaScript\\
  \textbf{Software:} & Git, \LaTeX\\
  \textbf{Packages:} & NumPy, Matplotlib, FLTK\\
  \textbf{Documentation:} & Doxygen, Sphinx\\
\end{tabular}

\section*{\textcolor{blue}{\LARGE Extracurricular}\xfilll[0pt]{0.5pt}}
\vspace{-8pt}

% {\bf \large Creative Field}  \vspace{-4pt}
\begin{itemize}[itemsep = -0.75 mm, leftmargin=*]
\vspace{-2pt}
	\item Successfully completed a course under the \textbf{National Sports
	Organization(NSO)}
	\hfill{\sl (Autumn 2021)}
    \item Designed a flying model of an \textbf{RC plane} powered by \textbf{BLDC motor} 
	\hfill{\sl (Autumn 2022)}
	\item Completed \LaTeX{} course in \textbf{Learner's Space}
	\hfill{\sl (Summer 2022)}

\end{itemize}
\vspace{-2pt}
  



\end{document}

