\documentclass[10 pt]{article}
\usepackage[a4paper,bottom = 10mm,left = 0.56in,right = 0.56in,top = 6.4mm]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{array}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{textcomp}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{verbatim}
\newcommand{\xfilll}[2][1ex]{
\dimen0=#2\advance\dimen0 by #1
\leaders\hrule height \dimen0 depth -#1\hfill}
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}
\renewcommand\labelitemi{\raisebox{0.4ex}{\tiny$\bullet$}}
\renewcommand{\labelitemii}{$\cdot$}
\pagenumbering{gobble}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    % pdftitle={Overleaf Example},
    % pdfpagemode=FullScreen,
    }
\begin{document}
\vspace*{50mm}
\hspace{-14pt}Pursuing \textbf{Honors} in \textbf{Computer Science} and {\bf Minor} in \textbf{Machine Intelligence and Data Science}
\vspace{-10pt}
\section*{\textcolor{blue}{\LARGE Scholastic Achievements}\xfilll[0pt]{0.5pt}}
\vspace{-8pt}
\begin{itemize}[itemsep = -0.75 mm, leftmargin=*]
\item Secured \textbf{All India Rank 232} in \textbf{JEE Advanced} among over 150 thousand candidates \hfill{\sl \small(2021)}
		\item Achieved \textbf{All India Rank 436} in \textbf{JEE Main} among over 1.2 million candidates \hfill{\sl \small(2021)}
		\item Secured \textbf{State Rank 48} in AP-EAMCET conducted by Andhra Pradesh State Council \hfill{\sl \small (2021)}
        \item Secured \textbf{State Rank 185} in TS-EAMCET conducted by Telangana State Council \hfill{\sl \small (2021)}
		\item Secured \textbf{All India Rank 364} in \textbf{KVPY} among over 50 thousand candidates \hfill{\sl \small(2020)}
\end{itemize}
%\vspace{-19pt}

\vspace{-22pt}
\section*{\textcolor{blue}{\LARGE Key Projects}\xfilll[0pt]{0.5pt}}
{\fontfamily{lmss}\selectfont
		\textbf{{Neural Quest}}\hfill{\sl \small (May-Present 2023)}\\
	}{\it Seasons of Code, Ongoing}\hfill{\sl \small Institute Technical Council, IIT Bombay}\\

		\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item  Researched, developed, implemented and evaluated diverse deep learning models for computer vision classification.
		\item Developed image prediction model for \textbf{MNIST} dataset from scratch using \textbf{NumPy} and \textbf{matplotlib} libraries
  and obtained an accuracy of \textbf{93} \% and \textbf{95} \% using \textbf{PyTorch} and \textbf{torchvision} evaluated on number of correct labels.
		\item Implemented classification model for CIFAR-10 using \textbf{convolutional neural network} and got accuracy of \textbf{81.28} \%.
		\item  Future plan to implement \textbf{Fast Gradient Sign Method (FGSM)} Attack on the \textbf{MNIST} image prediction model
	\end{itemize}
 {\fontfamily{lmss}\selectfont
		\textbf{{Blockchain Technology}}\hfill{\sl \small (May-Present 2023)}\\
	}{\it Summer of Science, Ongoing}\hfill{\sl \small Institute Technical Council, IIT Bombay}\\

		\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item  Studied basics of blockchain technology, including Bitcoin transaction security and defense against potential attacks.
  \item Studied \textbf{selfish mining attacks, Slasher}, and \textbf{PoS} in blockchain, Slasher penalizes, PoS validates based on staking.
  \item Exploring consensus algorithms such as \textbf{PBFT} and \textbf{Raft}, understanding their role in achieving fault-tolerance and consensus in distributed systems.
	\end{itemize}
 	{\fontfamily{lmss}\selectfont
		\textbf{{IPCP Prefetcher for Spec and Graph Workloads}}\hfill{\sl \small (spring 2023)}\\
	}{\it Guide: Prof. Biswa \textbar} {\it Course Project:  Computer Architecture}\hfill{\sl \small IIT Bombay}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Obtained an average 1.05x speedup in \textbf{IPC} on various traces by enhancing the \textbf{IPCP prefetcher} using \textbf{champsim}.
		\item Increased \textbf{cache hit rates} and \textbf{prefetch accuracy} in caches through customized modifications in IPCP prefetcher.
	\end{itemize}
{\fontfamily{lmss}\selectfont
		\textbf{{Cinema A to Z}}\hfill{\sl \small (Autumn '22)}\\
	}{\it Guide: Prof. Kavi Arya \textbar} {\it Course Project: Software Systems Lab}\hfill{\sl \small IIT Bombay}\\

		\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Developed a comprehensive movie and TV show database by utilizing \textbf{web scraping} techniques on IMDb, Rotten Tomatoes, extracting crucial data such as titles, ratings, genres, user reviews, similar movies, plot and cast information.
		\item Designed, executed, and successfully deployed an \textbf{SQL} database to efficiently store and manage the scraped data.
		\item Constructed a user-friendly website using \textbf{PHP}, allowing users to create accounts, log in, and personalize their movie watching experience by liking, watching, and adding or removing movies, TV shows, and anime to their watchlist.
		\item  Demonstrated proficiency in front-end development by designing an intuitive and visually appealing interface, enabling users to navigate through the vast collection of movies, TV shows, and anime, and interact with their  watchlist.
	\end{itemize}
{\fontfamily{lmss}\selectfont
		\textbf{{Rail Planner}}\hfill{\sl \small (Autumn 2022)}\\
	}{\it Guide: Prof. Supratik Chakraborty \textbar} {\it Ongoing Course Project}\hfill{\sl \small IIT Bombay}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Implemented multiple data structures and alogorithms in C++, including \textbf{Linked Lists, Dictionaries, Binary Search Trees, Tries},\textbf{Priority Queues}, and \textbf{BFS, DFS, KMP} and utilized each of them within suitable components.
\item Implemented {\bf graph} data structure to find the shortest route between two stations in the multi-rail network system.
\item Implemented an interface for rating and filtering system for the journey reviews using \textbf{Heap and Priority Queues}.
	\end{itemize}
  	{\fontfamily{lmss}\selectfont
		\textbf{{Goldreich Levin }}\hfill{\sl \small (spring 2023)}\\
	}{\it Guide: Prof. Manoj Prabhakaran \textbar} {\it Reading Project:  Cryptography \& Network security }\hfill{\sl \small IIT Bombay}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item  Studied about \textbf{hardcore predicates} for a \textbf{one way function, Markov’s inequality, pair-wise
independent randomness}, \textbf{Goldreich Levin} Theorem and its
proof in details along with an overview of \textbf{Chebychev’s inequality}.
	\end{itemize}
 \newpage
 \vspace{-16pt}
\section*{\textcolor{blue}{\LARGE Other Projects}\xfilll[0pt]{0.5pt}}
	{\fontfamily{lmss}\selectfont
		\textbf{{Best Offset Prefetcher}}\hfill{\sl \small (spring 2023)}\\
	}{\it Guide: Prof. Biswa \textbar} {\it Lab Assignment:  Computer Architecture Lab}\hfill{\sl \small IIT Bombay}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Successfully developed and integrated the best offset prefetcher using \textbf{Champsim}, a powerful simulation platform.
		\item Optimized memory access and reduced cache misses, resulting in improved system efficiency and faster data prefetching.
	\end{itemize}
 	{\fontfamily{lmss}\selectfont
		\textbf{{Sliding Puzzle}}\hfill{\sl \small (spring 2023)}\\
	}{\it Guide: Prof. Ashutosh Gupta \textbar} {\it Course Assignment:  Logic for Computer Science}\hfill{\sl \small IIT Bombay}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Developed SAT-based puzzle solver by implementing rules and constraints and finding optimal moves within limits.
		\item Implemented efficient Python algorithm using Z3 solver and added clauses for solving , showcasing logical reasoning.
	\end{itemize}
 	{\fontfamily{lmss}\selectfont
		\textbf{{Socket Programming: File transfer}}\hfill{\sl \small (Spring 2023)}\\
	}{\it Guide: Prof. Bhaskaran Raman \textbar} {\it Lab Assignment: Computer Networks Lab}\hfill{\sl \small IIT Bombay}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
    \item Implemented a \textbf{client to server} network for searching and downloading files in a specified topology using \textbf{sockets}.
    \item Incorporated \textbf{rate limiting} on the client-side for efficient handling of \textbf{multiple client} connections to the server.
	\end{itemize}
	{\fontfamily{lmss}\selectfont
		\textbf{{Tic-Tac-Toe}}\hfill{\sl \small (Autumn 2022)}\\
	}{\it Guide: Prof. Kavi Arya \textbar} {\it Lab Assignment: Software Systems Lab}\hfill{\sl \small IIT Bombay}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Developed a two-player Tic-Tac-Toe game using a Peer-to-Peer networking model, usiing the Socket and ServerSocket.
\item Implemented message exchange mechanisms between players using ports, enabling real-time gameplay and interaction.
\end{itemize}
	%\newpage
	{\fontfamily{lmss}\selectfont
		\textbf{{Portfolio Website}}\hfill{\sl \small (Autumn 2022)}\\
	}{\it Guide: Prof. Kavi Arya \textbar} {\it Lab Assignment: Software Systems Lab}\hfill{\sl \small IIT Bombay}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Designed user-friendly website on IITB CSE server using \textbf{SSH}, with various pages describing me and my projects.
		\item Used \textbf{HTML, CSS, Javascript, and Bootstrap} for developing the website and to make it responsive and interactive
	\end{itemize}
 	%\newpage
	{\fontfamily{lmss}\selectfont
		\textbf{{Random Walkers}}\hfill{\sl \small (Autumn 2022)}\\
	}{\it Guide: Prof. Suyash P. Awate \textbar} {\it Lab Assignment: Data Analysis and Interpretation}\hfill{\sl \small IIT Bombay}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Simulated N random walkers in \textbf{Numpy} and obtained the \textbf{Gaussian Distribution} plot of their final locations, verifying the \textbf{Law of Large Numbers} by comparing the true and computed mean and variance of the final positions.
	\end{itemize}
	{\fontfamily{lmss}\selectfont
		\textbf{{Maze Ball}}\hfill{\sl \small (Spring 2022)}\\
	}{\it Guide: Prof. Rushikesh K. Joshi \textbar} {\it Course Project : Abstractions and Paradigms}\hfill{\sl \small IIT Bombay}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Programmed an Maze Ball with the help of \textbf{FLTK library} by utilizing Inheritance and Event Handling techniques.
	\end{itemize}
\vspace{\baselineskip}
\vspace{-13pt}

\section*{\textcolor{blue}{\LARGE Technical Skills}\xfilll[0pt]{0.5pt}}
\vspace{-8pt}
\begin{tabular}{p{4.5cm} p{13.5cm}}
  \textbf{Programming:} &  C++, Python, Bash, Awk, Sed, Markdown, Java, Assembly, Prolog, FLTK\\
  \textbf{Web Development:} & HTML, CSS, Bootstrap, JavaScript\\
  \textbf{Software:} &  Git, \LaTeX, GDB, Sphinx, Doxygen, Jupyter, Docker, Wireshark\\
  \textbf{Packages:} & NumPy, Matplotlib, FLTK, Pandas, Torchvision, Pytorch\\
\end{tabular}
 \section*{\textcolor{blue}{\LARGE Courses Undertaken}\xfilll[0pt]{0.5pt}}
\vspace{-12pt}
\hspace{-5pt}
  \begin{tabular}{p{40mm} p{13.2cm}}
    \vspace{-3pt}\textbf{Computer Science:} & \vspace{-5pt}Cryptography and Network Security, Data Structures and Algorithms + Lab, Discrete Structures, Data Analysis and Interpretation, Software Systems Lab, Design and Analysis of Algorithms, Digital Logic Design + Lab, Computer Networks + Lab, Logic for Computer Science, Abstractions and Paradigms in Programming, Computer Programming and Utilization\\
    \vspace{-5pt}\textbf{Mathematics:} & \vspace{-5pt}Calculus, Linear Algebra, Differential Equations\\
    \vspace{-5pt}\textbf{Others:} & \vspace{-5pt}Introduction to Electrical and Electronics Circuits, Quantum Physics and Application, Basics of Electricity and Magnetism, Engineering Graphics and Drawing, Physical Chemistry, Organic and Inorganic Chemistry, Biology\\
  \end{tabular}
  \vspace{1pt}\\
\vspace{-10pt}

\section*{\textcolor{blue}{\LARGE Extracurricular}\xfilll[0pt]{0.5pt}}
\vspace{-8pt}

% {\bf \large Creative Field}  \vspace{-4pt}
\begin{itemize}[itemsep = -0.75 mm, leftmargin=*]
\vspace{-2pt}
	\item Successfully completed a course under the \textbf{National Sports
	Organization(NSO)}
	\hfill{\sl (Autumn 2021)}
	\end{itemize}
	{\fontfamily{lmss}\selectfont
		\textbf{{\LaTeX{} Bootcamp}}
	}\hfill{\sl (Summer 2022)}\\[-1pt]
	{\sl \textit{Learner’s Space \textbar }{\textit{ IIT Bombay}}}\\
	\begin{itemize}[itemsep = -0.8 mm, leftmargin=*]
		\vspace{-16pt}
		\item Implemented \LaTeX{} software to typeset technical and mathematical documents using a \textbf{workflow}
		\item Successfully completed \textbf{3} assignments based on \textbf{text formatting}, designing a \textbf{résumé} and typesetting
of a \textbf{technical document} having equations, matrices, tables and lines of programming languages
	\end{itemize}
	{\fontfamily{lmss}\selectfont
		\textbf{{RC Plane}}}
	 \hfill{\sl \small (Autumn 2022)}\\
{\it Aeromodelling Club}\hfill{\sl \small IIT Bombay}\\\vspace{-16pt}
\begin{itemize}[itemsep = -0.75 mm, leftmargin=*]
\item Constructed a remote controlled plane out of depron sheets keeping in mind the wing loading, wing shape, air drag, balance and weight for a perfect take off, flight and landing
  \end{itemize}
  \vspace{-2pt}
\vspace{-2pt}
\end{document}
